### 2019-04-28 report/overview.tex
Overview: outline for part III (applications of OT to ML problems...)

>>>>

\sect{Optimal Transport and Machine Learning}

\subs{Compute the optimal transport of what?}

Since Sinkhorn can be parallelized, one can compute a large amount of Optimal
Transport distances: for instance look into a database for similarity based
retrieval, blablabla

\paragraph{Color histograms}

For image retrieval blablabla...

\paragraph{Cloud of word}

For similar documents retrieval blabla

\subs{Wassersteinization}

Introduce Wasserstein distance into optimizations problem.

We show that we can computationaly differentiate, and therefore we can deal
with it in a variety of optimization problem, including machine learning
related opt. problems.

Somehow revisiting machine learning problems.

\paragraph{Averaging data}

histograms, distribution, images, experiments (repetition of same expriment,
MEG mesures, average over the experiments might be relevant)

\paragraph{Aggregating distributions}

From a very big dataset, split it in $J$ parts, learn the distribution (eg. w/
Bayesaian Learning) from each of the part in parralel (on $J$ machines):
the $J$ distributions should not be very different, but still the variance in
the data will cause some variation: the idea is to use Wasserstein averaging
to aggregate the distributions, and get a more meaningful one. Theoretic
guaranties! :D

Wasserstein posterior

%\subs{Semi-suppervised learning setting}

\paragraph{Semi-supervised learning setting}

Wasserstein propagation: smooth a graph $(V,E)$ where an histogram is associated
$\mu_v$ to each vertex $v$, with a susbset $S$ of the vertices that have a
fixed histogram (known data).

Solve the following optimization problem.

$$
    \underset{\substack{\mu_i \in \mathcal{P}\left(\Omega\right) \\ \text{for }i \in V\setminus S}}\min \sum_{(e_1, e_2) \in E} W_2^2\left(\mu_{e_1}, \mu_{e_2}\right)
$$

blabla

\paragraph{omg dictionnary learning what is this????????? :oooooo}

\subs{Wasserstein PCA, Geodesics and Inverse problem}

Since the space of distributions with the OT geometry has negative curvature,
we generalize the PCA (ie. projecting on one dimension spaces) into Generalized
Principal Geodesics. We then want to explain stuff out of what we found;
eg. affaire Bonneel vs nounours
